Universal Anonymous Signatures

### 2022-08-02 prism-backend/research/gsac/app-building-blocks.tex
Done with main pass after Markulf's comments.
Updating proofs.

\paragraph{Augmenting with NIZKs.} %
\todo{This is quite informal. Perhaps expand...} 
In the previous \SBCM scheme, it is straightforward to require that the party
running \SBCMCom proves some arbitrary claim over the messages to be signed
(both those in committed or plaintext form), as well as over possibly extra
auxiliary data. This can be done by having this party add a NIZK over the
corresponding NP statement, which has later to be verified by the party running
\SBCMSign.
%
We use this extension in our \CUASGen construction, and thus extend the previous
syntax for interactive signing  as follows, to account for an extra NIZK
relation \NIZKRel proving that a pair of statement $x$ and witness $w$ belong
\NIZKRel.

@@

\paragraph{OMF security.} The proof for OMF security is essentially the
same as that of EUF security for BBS+ signatures \cite{cdl16b}, which gives a
reduction against the $q$-SDH problem. There is only one exception: in the proof
for BBS+ EUF-security, when the adversary against EUF-security queries a
signature, the simulator (the adversary against $q$-SDH) has to simulate the
signature. For this, it requires the $l$ messages in the message set to be
signed, which in plain BBS+ it is not a problem, as they are received in the
clear. In the case of \SBCM, however, some of the messages to be signed are
received as part of a commitment. Note however that, in \SBCM, besides receiving
the commitment, we also receive a NIZK proof of knowledge of the corresponding
messages. Thus, the adversary against $q$-SDH in the OMF case only needs to
extract the witnesses from the proof. This is doable after soundness of NIZK.
If the NIZK also has online-extractability, then we do not need to impose
further requirements. If it is not, then the \SBCM scheme should not allow
parallel signing requests, or limit the total number of signatures to be
created to a logarithmic function of the security parameter (which is probably
not reasonable in most cases; although it may be for group signature-like
settings). We refer to \cite[Lemma 1]{cdl16b} for the full details of the proof
of EUF security in BBS+.
%
\jdv{If needed, do the actual proof. Should essentially be a copy-paste of
  that in \cite{cdl16b}...}

\paragraph{Blindness.} Blindness of \SBCM is a direct consequence of the
hiding property of the underlying block commitment scheme. Indeed, assume an
adversary $\adv$ against blindness of \SBCM. Then, $\adv$ can be used by
\advB against the hiding property of the commitment scheme in a straightforward
manner. That is, once $\adv$ outputs its two sets of messages to be signed in
committed form (i.e., $\overline{\smsg}_0$ and $\overline{\smsg}_1$, it feeds
them directly to its environment in \ExpComHideb; \advB awaits for the response
(a commitment of $\overline{\smsg}_b$), and forwards it to $\adv$. Finally,
\advB outputs whatever $\adv$ outputs. Clearly, if $\adv$ wins the blindness
game for \SBCM with non-negligible probability, so does \advB agains the hiding
game of the commitment scheme.

>>>>

\paragraph{Augmenting with NIZKs.} %
\todo{This is quite informal. Perhaps expand...} 
In the previous \SBCM scheme, it is straightforward to require that the party
running \SBCMCom proves, in zero knowledge, some arbitrary claim over the
messages to be signed (both those in committed or plaintext form), as well as
over possibly extra auxiliary data. This can be done by having this party add a
NIZK over the corresponding NP statement, which has later to be verified by the
party running \SBCMSign.
%
Clearly, if the base \SBCM scheme satisfies blindness, then extending it with a
zero-knowledge NIZK proof over the (blindly) signed messages, still maintains
blindness (the adversary cannot distinguish which committed messages set is
signed, in the blindness game).
%
We use this extension in our \CUASGen construction, and thus extend the previous
syntax for interactive signing  as follows, to account for an extra NIZK
relation \NIZKRel proving that a pair of statement $x$ and witness $w$ belong
\NIZKRel.

@@

\paragraph{OMF security.} The proof for OMF security is essentially the
same as that of EUF security for BBS+ signatures \cite{cdl16b}, which gives a
reduction against the $q$-SDH problem. There is only one exception: in the proof
for BBS+ EUF-security, when the adversary against EUF-security queries a
signature, the simulator (the adversary against $q$-SDH) has to simulate the
signature. For this, it requires the $l$ messages in the message set to be
signed, which in plain BBS+ it is not a problem, as they are received in the
clear. In the case of \SBCM, however, some of the messages to be signed are
received as part of a commitment. Note however that, in \SBCM, besides receiving
the commitment, we also receive a NIZK proof of knowledge of the corresponding
messages. Thus, the adversary against $q$-SDH in the OMF case only needs to
extract the witnesses from the proof. This is doable after soundness of NIZK.
If the NIZK also has online-extractability, then we do not need to impose
further requirements. If it is not, then the \SBCM scheme should not allow
parallel signing requests, or limit the total number of signatures to be
created to a logarithmic function of the security parameter (which is probably
not reasonable in most cases; although it may be for group signature-like
settings). We refer to \cite[Lemma 1]{cdl16b} for the full details of the proof
of EUF security in BBS+.
%
\jesus{If needed, do the actual proof. Should essentially be a copy-paste of
  that in \cite{cdl16b}...}

\paragraph{Blindness.} Blindness of \SBCM is a direct consequence of the
hiding property of the underlying block commitment scheme. Indeed, assume an
adversary $\adv$ against blindness of \SBCM. Then, $\adv$ can be used by
\advB against the hiding property of the commitment scheme in a straightforward
manner. That is, once $\adv$ outputs its two sets of messages to be signed in
committed form (i.e., $\overline{\smsg}_0$ and $\overline{\smsg}_1$, it feeds
them directly to its environment in \ExpComHideb; \advB awaits for the response
(a commitment of $\overline{\smsg}_b$), and forwards it to $\adv$. Finally,
\advB outputs whatever $\adv$ outputs. If $\adv$ wins the blindness
game for \SBCM with non-negligible probability, so does \advB against the hiding
game of the commitment scheme.

### 2022-08-02 prism-backend/research/gsac/app-uas-proofs.tex
Some deep syntax re-writing.
Updating proofs.

First, we define the \SimSetup, \ExtractIssue, \ExtractSign, \IdentifyCred and
\IdentifySig functions that are needed for some of the properties to be
meaningful, in \figref{fig:helper-funcs}.

\begin{figure}[ht!]
  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \procedure{$\SimSetup(1^\secpar)$}{%
        \textrm{Parse}~\secpar~\textrm{as}~(\Csecpar,\NIZKsecpar,\SBCMsecpar,
        \Esecpar). \\
        \Cparm \gets \CSetup(\Csecpar), \SBCMparm \gets  \SBCMSetup(\SBCMsecpar) \\
        \Sparm \gets \SSetup(\Ssecpar), \Eparm \gets \ESetup(\Esecpar) \\
        (\NIZKcrs_{\Issue},\trap_{\Issue}) \gets
        \NIZKSimSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar) \\
        (\NIZKcrs_{\Sign},\trap_{\Sign}) \gets
        \NIZKSimSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar) \\
        (\NIZKcrs_{\Open},\trap_{\Open}) \gets
        \NIZKSimSetup^{\NIZKRel_{\Open}}(\NIZKsecpar) \\
        \pcreturn ((\Cparm,\SBCMparm,\Sparm,\Eparm,\NIZKcrs_{\Issue},
        \NIZKcrs_{\Sign},\NIZKcrs_{\Open},\AttrSpace), \\
        \pcind (\trap_{\Issue},\trap_{\Sign},\trap_{\Open})) \\
      }

      \procedure{$\ExtractIssue(\parm,\trap,\utrans)$}{%
        \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Issue},\cdot,
          \cdot,\cdot)$} \\
        \textrm{Parse \trap as $(\trap_{\Issue},\cdot,\cdot)$, and
          \utrans as $(\Ccom,\sipk,\cred,\NIZKproof)$} \\
        \pcif \NIZKVerify^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},
        \NIZKproof,(\Ccom,\attrs,\sipk)): \pcreturn \bot \\
        (\usk,\scred,\attrs_{\scred}) \gets
        \NIZKExtract^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},
        \trap_{\Issue},
        (\Ccom,\attrs,\sipk),\NIZKproof) \\
        \pcreturn (\usk,\attrs,\scred,\attrs_{\scred}) \\
      }

      \procedure{$\ExtractSign(\parm,\trap,\oid,\siid,\sig,\yeval,\msg,\feval)$}{%
        \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Sign},
          \cdot)$} \\
        \textrm{Parse \trap as $(\cdot,\trap_{\Sign},\cdot)$, and
          \sig as $(\NIZKproof,\ceval,\cinsp)$} \\
        \textrm{Parse $\PUBOK[\oid]$ as $(\opk,\cdot)$ and let $\sipk \gets
          \PUBIK[\siid]$} \\
        \pcif \NIZKVerify^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKproof,
        (\msg,\feval,\yeval,\Ec,\sipk,\opk)): \pcreturn \bot \\
        (\usk,\scred,\attrs_{\scred},\yinsp,r) \gets
        \NIZKExtract^{\NIZKRel_{\Sign}}(\NIZKcrs^{\NIZKRel_{\Sign}},
        \NIZKtrap_{\Sign},
        (\msg,\feval,\yeval^0,\ceval,\cinsp,\sipk,\opk,\widetilde{\Eek}),
        \NIZKproof) \\
        \pcreturn (\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \\
      }

      % \procedure{$\IdentifyCred(\parm,\trap,\usk,\attrs_{\cred},\cred)$}{%
      %   \pcreturn \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) \\
      % }

      \procedure{$\IdentifyCred(\parm,\trap,\usk,\attrs_{\cred},\cred,\ipk)$}{%
        \pcreturn \SBCMVerify(\ipk,\cred,\usk,\attrs_{\cred}) \\
      }

      \procedure{$\IdentifySig(\parm,\trap,\usk,\scred,\Sig)$}{%
        \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
        \pcfor \cid~\suchthat~\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot) \\
        \pcind (\usk',\cdot,\cdot,\cdot) \gets \ExtractIssue(\parm,\trap,\trans[\cid]) \\
        \pcind \pcif \usk = \usk': \pcreturn 1 \\
        \pcreturn 0
      }

      % \procedure{$\IdentifySig(\parm,\trap,\uid,\usk)$}{%
      %   \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
      %   \pcfor \cid~\suchthat~\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot) \\
      %   \pcind (\usk',\cdot,\cdot,\cdot) \gets \ExtractIssue(\parm,\trap,\trans[\cid]) \\
      %   \pcind \pcif \usk = \usk': \pcreturn 1 \\
      %   \pcreturn 0
      % }

    \end{minipage}
  }
  \label{fig:helper-funcs}
  \caption{Definition of helper functions \ExtractIssue, \ExtractSign,
    \IdentifyCred, and \IdentifySig, for \CUASGen.}
\end{figure}

@@

\begin{proof}[\thmref{thm:issue-anonymity-uas}; Issuance anonymity of \CUASGen]
  We prove the special case in which the adversary makes only one query to the
  \OBTCHALb oracle. The generalization to polynomially many queries follows from
  a standard hybrid argument.

  Let $G_0=\ExpIssAnonb(1^\secpar)$. We define $G_1$ by replacing the calls to
  \NIZKSetup in $G_0$, for the $\NIZK^{\Issue}$ and $\NIZK^{\Sign}$ systems by
  calls to their corresponding \NIZKSimSetup. By zero-knowledgeness of the
  NIZKs, both games are indistinguishable.

  Next, we simulate the NIZK proofs produced by \Obtain within the \OBTCHALb
  oracle and, consequently, the NIZK proofs produced by \Sign in \SIGN for
  signatures from the challenge user and credentials. Then, we show that the
  adversary cannot distinguish executions for $b=0$ from executions for $b=1$,
  except with negligible probabability.

  More concretely, on the one hand, let $G_1^0$ to be $G_1$, conditioned on
  $b=0$. Concretely, the proofs sent by the challenge user $\cuid_0$ to the
  adversarial issuer are of
  the form $\pi^*_0 =\NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\UK[\cuid_0],
  \CCRED[\cscid_0],\ATTR[\cscid_0],r),(\Ccom,\attrs,\PUBIK[\cscid_0]))$. The
  NIZK proofs included in the signatures produced by $\cuid_0$ are defined
  correspondingly, but for $\NIZK^{\NIZKRel_{\Sign}}$. From $G_1^0$, we define
  $G_2^0$, but instead of using \NIZKProve, we use \NIZKSim (for both \Issue
  and \Sign). That is, the proofs for credential requests are generated as
  $\pi^s_0 =\NIZKSim^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},\tau,(\Ccom,\attrs,
  \PUBIK[\cscid_0]))$. By zero-knowledge of the NIZK systems for \Issue and
  \Sign, $G_2^0$ is indistinguishable from $G_1^0$.

  On the other hand, following the same process for $G_1^1$ and $G_2^1$.
  Concretely, for the case of the proofs at issuance time, they are of the
  shape $\pi^s_1 =\NIZKSim^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},\tau,(\Ccom,\attrs,
  \PUBIK[\cscid_1]))$. Note first that $\PUBIK[\cscid_1] = \PUBIK[\cscid_0]$,
  by definition of the \OBTCHALb oracle. Hence, the produced proofs are exactly
  the same independently on the value of the bit $b$.

  Thus, $\AdvIssAnon=|\Pr\lbrack
  \ExpIssAnono(1^\secpar)=1\rbrack-\Pr\lbrack\ExpIssAnonz(1^\secpar)=1\rbrack|$.
  As argued, $G_1$ is indistinguishable from $\ExpIssAnonb$, so
  $\AdvIssAnon \approx |\Pr\lbrack G_1^1(1^\secpar)=1\rbrack-\Pr\lbrack
  G_1^0(1^\secpar)=1\rbrack| \approx
  |\Pr\lbrack G_2^1(1^\secpar)=1\rbrack-\Pr\lbrack
  G_2^0(1^\secpar)=1\rbrack|$. Since $G_2^1=G_2^0$, it follows that
  \AdvIssAnon is negligible.

\end{proof}

>>>>

\todo{Do we only need this for \fissue function?}
First, we formally define now what do we mean with \UAS-acceptable \fissue,
complementing the informal \defref{def:uas-acc-func}.

\begin{figure}[ht!]
  \centering  
  \scalebox{0.9}{
    \procedure{$\Exp^{\UAS-acc-b}_\adv(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      \pcfor d\in\bin: \\
      \pcind (\upk_d,\usk_d) \gets \KeyGen(\parm) \\
      \pcind (\st,\attrs, \lbrace (\cidi_d,\cidu_d,\cattrs_{d,i}) \rbrace_{i\in[n]})
      \gets \adv(\st,\upk_0,\upk_1) \\
      \yissue^* \gets \fissue(\upk_b,
      \lbrace (\cidi_b,\cattrs_{b,i}) \rbrace_{i\in[n]},
      \attrs) \\
      b^* \gets \adv(\st,\yissue*) \\
      \pcreturn b=b^*
    }
  }
  \label{fig:uas-acceptable}
  \caption{Formal definition of \UAS-acceptable \fissue functions.}
\end{figure}

Next, we define the \SimSetup, \ExtractIssue, \ExtractSign functions. \SimSetup
(formally defined in \figref{fig:helper-funcs}).essentially replaces the
\Setup algorithm of each NIZK with the corresponding \NIZKSimSetup algorithm,
and returns the generated parameters along with the
trapdoors. \ExtractIssue and \ExtractSign simply run the \Extract functions
of the corresponding \NIZK scheme, leveraging the trapdoor produced during
\SimSetup. Note that, due to the zero-knowledge and simulation extractability
properties (respectively) of the underlying NIZKs, the result of \SimSetup
is indistinguishable from that of \Setup, and the extracted values match those
used as witnesses in the proofs.

\begin{figure}[ht!]
  \centering  
  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \procedure{$\SimSetup(1^\secpar)$}{%
        \textrm{Parse}~\secpar~\textrm{as}~(\Csecpar,\NIZKsecpar,\SBCMsecpar,
        \Esecpar). \\
        \Cparm \gets \CSetup(\Csecpar), \SBCMparm \gets  \SBCMSetup(\SBCMsecpar) \\
        \Sparm \gets \SSetup(\Ssecpar), \Eparm \gets \ESetup(\Esecpar) \\
        (\NIZKcrs_{\Issue},\trap_{\Issue}) \gets
        \NIZKSimSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar) \\
        (\NIZKcrs_{\Sign},\trap_{\Sign}) \gets
        \NIZKSimSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar) \\
        (\NIZKcrs_{\Open},\trap_{\Open}) \gets
        \NIZKSimSetup^{\NIZKRel_{\Open}}(\NIZKsecpar) \\
        \pcreturn ((\Cparm,\SBCMparm,\Sparm,\Eparm,\NIZKcrs_{\Issue},
        \NIZKcrs_{\Sign},\NIZKcrs_{\Open},\AttrSpace), \\
        \pcind (\trap_{\Issue},\trap_{\Sign},\trap_{\Open}))
      }

      % \procedure{$\ExtractIssue(\parm,\trap,\utrans)$}{%
      %   \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Issue},\cdot,
      %     \cdot,\cdot)$} \\
      %   \textrm{Parse \trap as $(\trap_{\Issue},\cdot,\cdot)$, and
      %     \utrans as $(\Ccom,\sipk,\cred,\NIZKproof)$} \\
      %   \pcif \NIZKVerify^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},
      %   \NIZKproof,(\Ccom,\attrs,\sipk)): \pcreturn \bot \\
      %   (\usk,\credid,\scred,\attrs_{\scred}) \gets
      %   \NIZKExtract^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},
      %   \trap_{\Issue},
      %   (\Ccom,\attrs,\sipk),\NIZKproof) \\
      %   \textrm{Let \credid be}~\suchthat~\trans[\credid] = \utrans;
      %   \uid \gets \OWNR[\credid] \\        
      %   \pcif \uid \in \HU \land \UK[\uid] \neq \usk: \pcreturn \bot \\
      %   \pcelse: \\
      %   \pcind \pcif \UK[\uid] = \bot: \UK[\uid] \gets \usk \\
      %   \pcind \pcelse \pcif \UK[\uid] \neq \usk: \pcreturn 0 \\
      %   \pcreturn (\uid,\usk,\credid,\scred,\attrs_{\scred}) \\
      % }

      % \procedure{$\ExtractSign(\parm,\trap,\oid,\siid,\sig,\yeval,\msg,\feval)$}{%
      %   \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Sign},
      %     \cdot)$} \\
      %   \textrm{Parse \trap as $(\cdot,\trap_{\Sign},\cdot)$, and
      %     \sig as $(\NIZKproof,\ceval,\cinsp)$} \\
      %   \textrm{Parse $\PUBOK[\oid]$ as $(\opk,\cdot)$ and let $\sipk \gets
      %     \PUBIK[\siid]$} \\
      %   \pcif \NIZKVerify^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKproof,
      %   (\msg,\feval,\yeval,\Ec,\sipk,\opk)): \pcreturn \bot \\
      %   (\usk,\scredid,\scred,\attrs_{\scred},\yinsp,r) \gets
      %   \NIZKExtract^{\NIZKRel_{\Sign}}(\NIZKcrs^{\NIZKRel_{\Sign}},
      %   \NIZKtrap_{\Sign},
      %   (\msg,\feval,\yeval^0,\ceval,\cinsp,\sipk,\opk,\widetilde{\Eek}),
      %   \NIZKproof) \\
      %   \pcif \exists \uid \in \HU~\suchthat~\UK[\uid] = \usk: \\
      %   \pcreturn (\uid,\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \\
      %   \pcelse \textrm{\todo{Need to add \cid as explicit attribute to the
      %       credentials (chosen by issuer) so that can bookkeep.}} \\
      %   \pcelse \textrm{\todo{then adapt the rest}} \\
      %   \pcind \pcelse \pcif \UK[\uid] \neq \usk: \pcreturn 0 \\
      %   \pcreturn (\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \\
      % }

      % % \procedure{$\IdentifyCred(\parm,\trap,\usk,\attrs_{\cred},\cred)$}{%
      % %   \pcreturn \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) \\
      % % }

      % \procedure{$\IdentifyCred(\parm,\trap,\usk,\attrs_{\cred},\cred,\ipk)$}{%
      %   \pcreturn \SBCMVerify(\ipk,\cred,\usk,\attrs_{\cred}) \\
      % }

      % \procedure{$\IdentifySig(\parm,\trap,\usk,\scred,\Sig)$}{%
      %   \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
      %   \pcfor \cid~\suchthat~\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot) \\
      %   \pcind (\usk',\cdot,\cdot,\cdot) \gets \ExtractIssue(\parm,\trap,\trans[\cid]) \\
      %   \pcind \pcif \usk = \usk': \pcreturn 1 \\
      %   \pcreturn 0
      % }

      % % \procedure{$\IdentifySig(\parm,\trap,\uid,\usk)$}{%
      % %   \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
      % %   \pcfor \cid~\suchthat~\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot) \\
      % %   \pcind (\usk',\cdot,\cdot,\cdot) \gets \ExtractIssue(\parm,\trap,\trans[\cid]) \\
      % %   \pcind \pcif \usk = \usk': \pcreturn 1 \\
      % %   \pcreturn 0
      % % }

    \end{minipage}
  }
  \label{fig:helper-funcs}
  \caption{Definition of helper function \SimSetup, for \CUASGen.}
\end{figure}

@@

\begin{proof}[\thmref{thm:issue-anonymity-uas}; Issuance anonymity of \CUASGen]
  % We prove the special case in which the adversary makes only one query to the
  % \OBTCHALb oracle. The generalization to polynomially many queries follows from
  % a standard hybrid argument.

  First, observe that, excluding the \yissue value output revealed to the issuer
  during the interactive issuance protocol, \CUASGen essentially runs an
  interactive signing protocol of an \SBCM scheme, augmented with a
  zero-knowledge NIZK for $\NIZKRel_{\Issue}$. As stated in \appref{sapp:sbcm},
  blindness of the (non-augmented) \SBCM scheme, and the zero-knowledge property
  of the NIZK for $\NIZKRel_{\Issue}$, ensure that the challenge credentials are
  indistinguishable between thesmselves. Concretely, we can replace the NIZK
  proofs sent by the user by simulated proofs.

  Finally, note that, to avoid trivial wins by the adversary, the issuance
  anonymity game requires that \fissue either rejects (returns $\yissue=0$) for
  both challenge users, or it accepts for both (returns $\yissue \neq 0$).
  Moreover, in the latter case, since we require that \fissue functions are
  \UAS-acceptable functions, the resulting \yissue value is hiding with respect
  to the input arguments. Thus, adding \yissue does not allow the adversary to
  distinguish credential issuance protocols.  
\end{proof}
